Tailoring Differentially Private Bayesian Inference to Distance Between Distributions

### 2018-10-24 Arxiv/main.tex
fix typo

By setting the $\gamma$ as $\ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 (n + 1)})})$, $\hexpmech$ is $(\epsilon, \delta) -$differentially private, where $\delta = \frac{e^{\frac{\epsilon}{2}} \delta'}{2}$. (or $\gamma = \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 |\candidateset|})})$ when generalized to Dirichlet-multinomial System)

@@

		\begin{equation*}
		\begin{split}
		|r|  \frac{exp(\frac{\epsilon (\hat{s} + \delta')}{2 S(\dataobs)})}{NL(\dataobs)} \cdot e^{\frac{- \epsilon \delta'}{2 S(\dataobs)}}
		& |r| \leq \frac{exp(\frac{\epsilon (\hat{s} + \delta')}{2 S(\dataobs)})}{NL(\dataobs)} \cdot e^{\frac{\epsilon}{2}}\\
		&  =  e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(r,x) = (\delta' + \hat{s})] \leq RHS\\
		\end{split}
		\end{equation*}

@@

	\begin{equation*}
	\begin{split}
	\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[ z = r]
	& = 	\frac{1}{|z|}\Big( \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[ u(x,z) = U]\Big)\\
	& \leq 	\frac{1}{|z|}\Big( e^{\epsilon / 2} \cdot \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[ u(x,z) = U_2]\Big)\\
	& \leq 	\frac{1}{|z|}\Big( e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[ u(x,z) = U_3] + e^{\epsilon/2} \cdot \frac{\delta'}{2}\Big)\\
	& = 	\frac{1}{|z|}\Big( e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(\dataobs')}{Pr}[ u(y,z) = U] + \frac{e^{\epsilon/2} \delta'}{2}\Big) \\
	& = e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[ z = r] + \delta,
	\end{split}
	\end{equation*}
	where the $\delta = \frac{e^{\epsilon/2} \delta'}{2|z|}$.

@@

Since $\delta$ takes the maximum value, i.e., $\frac{e^{\frac{\epsilon}{2}} \delta'}{2}$.
\end{proof}

>>>>

By setting the $\gamma$ as $\ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 (n + 1)})})$, $\hexpmech$ is $(\epsilon, \delta) -$differentially private, where $\delta = \frac{e^{\frac{\epsilon}{2}} \delta'}{2}$.

@@

		\begin{equation*}
		\begin{split}
		|r|  \frac{exp(\frac{\epsilon (\hat{s} + \delta')}{2 S(\dataobs)})}{NL(\dataobs)} \cdot e^{\frac{- \epsilon \delta'}{2 S(\dataobs)}}
		&  \leq |r| \frac{exp(\frac{\epsilon (\hat{s} + \delta')}{2 S(\dataobs)})}{NL(\dataobs)} \cdot e^{\frac{\epsilon}{2}}\\
		&  =  e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(r,x) = (\delta' + \hat{s})] \leq RHS\\
		\end{split}
		\end{equation*}

@@

	\begin{equation*}
	\begin{split}
	\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[ z = r]
	& = 	\frac{1}{|z|}\Big( \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[ u(x,z) = U]\Big)\\
	& \leq 	\frac{1}{|z|}\Big( e^{\epsilon / 2} \cdot \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[ u(x,z) = U_2]\Big)\\
	& \leq 	\frac{1}{|z|}\Big( e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[ u(x,z) = U_3] + e^{\epsilon/2} \cdot \frac{\delta'}{2}\Big)\\
	& = 	\frac{1}{|z|}\Big( e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(\dataobs')}{Pr}[ u(y,z) = U] + \frac{e^{\epsilon/2} \delta'}{2}\Big) \\
	& = e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(\dataobs')}{Pr}[ z = r] + \delta,
	\end{split}
	\end{equation*}
	where the $\delta = \frac{e^{\epsilon/2} \delta'}{2|z|}$.

@@

 $\delta$ takes the maximum value, i.e., $\frac{e^{\frac{\epsilon}{2}} \delta'}{2}$.
\end{proof}
